Analysing the Factors Influencing the Wages of the US Workforce in 2023

### 2024-12-03 paper/paper.qmd
Final commit

This study use Multiple Linear Regression (MLR) to model the relationship between income and various predictors, carried out with the `lm` function in R [@citeR]. The dataset is divided into training and testing sets using the `createDataPartition` function from the `caret` [@caret] package, with 60% allocated for model training and parameter estimation and 40% for testing to evaluate predictive performance.

>>>>

This study use Multiple Linear Regression (MLR) to model the relationship between income and various predictors, carried out with the `lm` function in R [@citeR]. The dataset is divided into training and testing sets using the `createDataPartition` function from the `caret` package [@caret], with 60% allocated for model training and parameter estimation and 40% for testing to evaluate predictive performance.
